Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-09 manuscript/manuscript.Rmd
added figure thought

Figure 1: 1-D and 3-D model conceptual figure. something about the objective / decision
Figure 2: Stability / multistability in the 1D and 3D models.  state space + time views

Figure 3: The 1-D optimal management solution.  'constant escapement' intuition etc

@@

>>>>

Figure 0: contrast 1D vs 3D strategies (see commented out diagram).

<!-- Reality __
  |        \
  v         \
1-D Model   More expressive model
  |                  |
  v                  v
Optimal        Suboptimal, but
solution   well-performing solution -->

Figure 1: 1-D and 3-D model conceptual figure. something about the objective / decision
Figure 2: Stability / multistability in the 1D and 3D models.  state space + time views
Figure 3: The 1-D optimal management solution.  'constant escapement' intuition etc

@@

Here we review classical strategies for sustainable fishery management and we provide a birds-eye view of the alternative approach we propose.
A summary of the contrast between the two strategies is given in Fig. \ref{tbd}.

## Classical strategies: MSY, escapement, total allowable catch
